Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2012-06-25 3dimpvt/paper.tex
progress

Since indoor environments often contain repetitive features such as
floor tiles or doors, we need to ensure that our SIFT-based distances
are reliable. In order to mitigate the effect of incorrect matches and
outliers, the RANSAC framework \cite{fischler1981random} is used for a
robust estimate of the optimal $dx$ and $dy$ distances between two
images. The RANSAC framework handles the consensus-building machinery,
and requires a fitting function and a distance function. For this
application, the fitting function simply finds the average distance
between matches in a pair of images. Our distance function for a pair
of points is the difference between those points' SIFT match distance
and the average distance computed by the fitting function; we use a 10
pixel outlier threshold. This means that a SIFT match is labeled as an
outlier if its horizontal or vertical distance is not within 10 pixels
of the average distance computed by the fitting function.

\subsubsection{Refining Image Positions using Least Squares}
\label{sec:refiningImagePositions}
There are a total of $M^{2}$ possible pairs of images, though we only
generate distances between images that overlap at SIFT feature
points. Given these distances and the original image location
estimates, we can solve a least squares problem
($\textrm{min}_{\vec{\beta}} ||X \vec{\beta} - \vec{\gamma}||_2^2 $)
to estimate the correct location of the images on the plane. The
$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$ and
$y$ locations of each image on the plane from $1 \dots M$. The optimal
$x$ and $y$ locations are obtained in the same way, so we only
consider the $x$ locations here:

@@

The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row
for each pair of images with measured distances produced by the SIFT
matching stage. A row in the matrix has a $-1$ and $1$ in the columns
corresponding to the two images in the pair. For example, the matrix
below indicates that we generated a SIFT-based distance between images
1 and 2, images 1 and 3, images 2 and 3, etc.

\[
X =
\begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
  0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\
  0 & 0 & 0 & \cdots & -1 & 1 \\
  1 & 0 & 0 & \cdots & 0 & 0 \\
\end{pmatrix}
\]

@@

Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
constructed using the SIFT-based distances generated earlier in the
matching stage. The distances are denoted as $d_1 \dots d_N$ for $N$
SIFT-based distances. The last element in the observation vector is
the location of the first image determined by its original noisy
localization, from \cite{chen2010indoor, liu2010indoor}:

\[
\vec{y}^T =
\begin{pmatrix}
  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
\end{pmatrix}
\]

The $\vec{\beta}$ that minimizes $||X \vec{\beta} -
\vec{\gamma}||_2^2$ results in a set of image locations on the plane
that best honors all the SIFT-based distance measurements between
images. In practice there are often cases where there is a break in
the chain of images, meaning that no SIFT matches were found between
one segment of the plane and another. In this case we add rows to the
$X$ matrix and observations to the $\vec{\gamma}$ vector that contain
the original noisy $x$ and $y$ distance estimates generated by the
localization algorithm \cite{chen2010indoor, liu2010indoor}. Another
way to do this is to add rows for all neighboring pairs of images and
solve a weighted least squares problem where the SIFT distances are
given a higher weight i.e. 1, and the noisy distances generated by the
localization algorithm \cite{chen2010indoor, liu2010indoor} are given
a smaller weight i.e. 0.01.

After completing this same process for the $y$ dimension as well, and
making the resultant shifts, our images overlap and match each other
with far greater accuracy. Applying the tile caching method from
Section \ref{sec:mappingWithCaching} on these re-localized images
results in the significant improvements shown in Figure
\ref{fig:compareAll}(c), as compared to Figure \ref{fig:compareAll}(d).

\subsection{Texture Mapping with Seam Minimization}
\label{sec:seamMinimization}

\begin{figure}
  \centering
  \includegraphics[width=3in]{highCameraAngle.pdf}
  \caption{(1) projects perpendicularly onto a wall and provides
    uniformly high resolution textures over its entire projection
    (2). (3) on the other hand projects at a poor angle onto the
    ceiling (4), resulting in usable texture at point A, but
    increasingly low resolution texture towards point B.}
  \label{fig:highCameraAngle}
\end{figure}

As mentioned earlier, our backpack system has 2 cameras with
$180^\circ$ fisheye lenses facing to the right and left. Since the
backpack operator only takes care to fully scan each wall and not
necessarily the entirety of each ceiling and floor, cameras at higher
angles with respect to plane normal vectors must be used for texturing
large areas of floor and ceiling planes. These high camera angles
translate into images that span extremely large areas once
projected. Such image projections have good scores (from Figure
\ref{fig:scoringFunction}) for certain areas on the plane, but much
worse scores for other areas. This can be seen in Figure
\ref{fig:highCameraAngle}. The tiling approach used in Section
\ref{sec:simpleTextureMapping} was thus a good choice for texturing,
as it allowed us to only use the parts of image projections that were
good choices for their respective plane locations, e.g. areas near
point A in Figure \ref{fig:highCameraAngle}, but not near point B.

For wall planes however, we have images all taken from close distances
and more head-on angles, and thus higher resolution, near-rectangular
projections to work with. As a result, there is less deviation over
the score of each tile within an image, as well as over the average
scores of all images. This means that the scoring criteria from Figure
\ref{fig:scoringFunction} is less relevant to walls, which enjoy an
abundance of head-on images.

Thus, for planes with optimal images, rather than selecting the set of
best images, since all images are near in quality, we instead select
the best set of images, such that the selection together results in
the cleanest final texture. We will accomplish this by using entire
images where possible, and defining a cost function to minimize the
visibility of seams in our final texture.

\subsubsection{Occlusion Masking}
\label{sec:occlusionMasking}
To begin with, we need to ensure that our images contain only content
that should be mapped onto the target plane in question. The tiling
approach used previously only checks occlusion for each tile as it is
being textured. For our new approach, we prefer entire images, so we
need to perform occlusion checks over the entirety of each image to
determine available areas for texture mapping.

Fortunately, by virtue of our indoor environments, the vast majority
of surface geometry is either horizontal or vertical, with high
amounts of right angles. This means that after masking out occluded
areas, our image projections will remain largely rectangular. We can
thus be efficient by recursively splitting each image into rectangular
pieces, and performing the same occlusion checks used in the tiling
process where needed. To actually occlude out rectangles, we simply
remove their texture, as we will ensure that untextured areas are
never chosen for texture mapping.

\subsubsection{Image Selection}
\label{sec:imageSelection}
To determine the set of images that results in the cleanest texture,
we need a cost function to evaluate the visibiilty of seams between
images in our set. A straightforward cost function that accomplishes
this is the sum of squared pixel differences in overlapping regions
between all pairs of images, after they have been aligned as described
in Section \ref{sec:projectionAndRotation}. Minimizing this cost
function encourages image boundaries to occur either in featureless
areas, such as bare walls, or in areas where images match extremely
well.

With the cost function defined, we must now select the set of images
for which the overall cost function is minimized. Since nearly all the
images for these optimal cases are head on, the best strategy to
minimize seams is to choose as few images as possible while texturing
a given plane. Thus,to cover the entirety of a plane, our problem can
be defined as minimally covering a polygon i.e. the plane, using other
polygons of arbitrary geometry i.e. our image projections, with the
added constraint of minimizing our cost function between chosen
images.  This is a complex problem, though we can take a number of
steps to simplify it. Given that our wall-texture candidate images are
all taken from a head-on angle, and assuming only minor rotations are
made during localization refinement, we can reason that their
projections onto the plane are approximately rectangular, as in Figure
\ref{fig:highCameraAngle}. By cropping them all to be rectangular, our
problem becomes the conceptually simpler one of filling a polygon with
rectangles, such that the sum of all edge costs between each pair of
rectangles is minimal. We thus also retain the advantages of working
with rectangular units, as explained in Section
\ref{sec:simpleTextureMapping}.

The location and orientation of the cameras on our backpack is such
that our images nearly always contain the entirety of the floor to
ceiling range of wall planes. Images are therefore rarely projected
with one above another when texturing wall planes, which correspond to
the optimal case we are working with.  In essence, we need only to
ensure horizontal coverage of our planes, as our images provide full
vertical coverage themselves. We can thus construct a Directed Acyclic
Graph (DAG) from the images, with edge costs defined by our cost
function above, and solve a simple shortest path problem to find an
optimal subset of images with regard to the cost functions
\cite{dijkstra}.

@@

Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
from overlapping images of a long hallway. Images are sorted by
horizontal location left to right, and become nodes in a
graph. Directed edges are placed in the graph from left to right
between images that overlap. The weights of these edges are determined
by the cost functions discussed previously. Next, we add two
artificial nodes, one start node representing the left border of the
plane, and one end node representing the right border of the
plane. The left(right) artificial node has directed edges with equal
cost $C_0$ to(from) all images that meet the left(right) border of the
plane.

@@

In rare cases where the vertical dimension of the plane is not
entirely covered by one or more chosen images, we are left with holes
where no images are selected to texture. To address this, we simply
modify the edges chosen by our shortest path solution such that they
have higher cost than all other edges in our DAG, and solve for a new
shortest path. This ensures that these edges will not be chosen again
unless they are the only available option. Our second shortest path
solution will result in a new set of chosen images, of which we only
retain those that cover areas not covered by the first set. This
process can be repeated as many times as needed, until holes are no
longer present. This method is not as optimal as a 2D-coverage
solution would be, but it is a quick approximation, and adequately
handles the few holes we run into.

With this completed, we have now mapped every location on our plane to
at least one image, and have minimized the number of images, as well
as the discontinuities between their borders. In the next section, we
apply blending between images where they overlap, but for the sake of
comparison with the unblended tile caching method in Section
\ref{sec:mappingWithCaching}, we arbitrarily choose one image for
texturing where images overlap. Figures \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d)
compare the tile caching method against this seam minimization
method.

Though both methods provide quite accurate texturing thanks to the
alignment process, the seam minimization approach results in fewer
visible discontinuities, since it directly reduces the cost of each
image boundary, while the tile caching method uses a scoring function
that only approximates this effect. Furthermore, seam minimization
guarantees the best selection of images, while the sequential tile
caching method may select images early on that turn out to be poor
choices once subsequent tiles have been processed. The seam minimization approach is also less intensive in terms of memory usage and runtime, as it does not require discretizing planes or images.

In the context of the backpack modeling system, we apply the seam
minimization approach on walls, due to its superior output when
provided with head-on images. Floors and ceilings however, given their
many images taken at oblique angles, as shown in Figure
\ref{fig:highCameraAngle}, are textured using the tile caching method.

\subsection{Blending}
\label{sec:blending}
We now apply the same blending process on our two texturing methods:
localization refinement followed by either tile caching or seam
minimization for texturing.

Although our preprocessing steps and image selections in either method
attempt to minimize all mismatches between images, there are sometimes
unavoidable discontinuities in our final texture due to different
lighting conditions or inaccuracies in planar geometry or
projection. These can however be treated and smoothed over by applying
alpha blending over image seams.  Whether the units we are blending
are rectangularly-cropped images or rectangular tiles, we can apply
the same blending procedure, as long as we have a guaranteed overlap
between units to blend over.

For the tile caching method, we can ensure overlap by texturing a
larger tile than needed for display. For example, for a rendered tile
$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
\times (l_1 + l_2)$ in size. For the seam minimization method, we have
already ensured overlap between images. To enforce consistent blending
however, we add a minimuum required overlap distance while solving the
shortest path problem in Section
\ref{sec:imageSelection}. Additionally, if images overlap in a region
greater than the overlap distance, we only apply blending over an area
equal to the overlap distance.

After blending pixels linearly across overlapping regions using alpha
blending, our texture mapping is complete. Figure
\ref{fig:pipelineimages} shows each incremental step of our texture
mapping approach, as well as the final blended output resulting from
both of our methods.

@@

\section{Results and Conclusions}
\label{sec:resultsAndConclusions}
In this paper, we have developed an approach to texture map models
with noisy camera localization data. We are able to refine image
locations based on feature matching, and robustly handle outliers.  We
generalized one texture mapping approach to any manner of planes and
images, and successfully textured both simple rectangular walls as
well as complex floor and ceiling geometry. We also presented an
optimized texturing method that takes advantage of our localization
refinement process and produces more seamless textures on planes where
multiple head-on images are available. Each of these approaches is
highly modular, and easily tunable for different environments and
acquisition hardware.

Ceilings and floors textured with the tile caching approach, and walls
textured with the seam minimization approach, are displayed in Figure
\ref{fig:results}. High resolution texture comparisons, as well as a
walkthrough of a fully textured 3D model are available in the
accompanying video to this paper.

>>>>

Since indoor environments often contain repetitive features such as
floor tiles or doors, we need to ensure that our SIFT-based distances
are reliable. In order to mitigate the effect of incorrect matches and
outliers, the RANSAC framework \cite{fischler1981random} is used for a
robust estimate of the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
images $i$ and $j$. The RANSAC framework handles the consensus-building machinery,
and requires a fitting function and a distance function. For this
application, the fitting function simply finds the average distance
between matches in a pair of images. The distance function for a pair
of points is chosen to be the difference between those points' SIFT match distance
and the average distance computed by the fitting function; we use a 10
pixel outlier threshold. This means that a SIFT match is labeled as an
outlier if its horizontal or vertical distance is not within 10 pixels
of the average distance computed by the fitting function.

We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair of images to refine their positions using least squares. Recall that there are a total of $M^{2}$ possible pairs of images, though we only
generate distances between images that overlap at SIFT feature
points. Given these distances and the original image location
estimates, we can solve a least squares problem
($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
to estimate the location of the images on the plane. The
$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$ location of each image on the plane for $1 \dots M$. The optimal
$x$ and $y$ locations are obtained in the same way, so we only
consider the $x$ locations here:

@@

The $N \times (M+1)$ dimensional matrix $A$ is constructed with one row
for each pair of images with measured distances produced by the SIFT
matching stage. A row in the matrix has a $-1$ and $1$ in the columns
corresponding to the two images in the pair. For example, the matrix
below indicates that we generated a SIFT-based distance between images
1 and 2, images 1 and 3, images 2 and 3, etc.

\[
A =
\begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
  0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\
  0 & 0 & 0 & \cdots & -1 & 1 \\
  1 & 0 & 0 & \cdots & 0 & 0 \\
\end{pmatrix}
\]

@@

Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
constructed using the SIFT-based distances generated earlier in the
RANSAC matching stage. The last element in the observation vector is
the location of the first image determined by its original noisy
localization, from \cite{chen2010indoor, liu2010indoor}. Thus $\vec{\gamma}$ can be written as:

\[
\vec{\gamma}^T =
\begin{pmatrix}
  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
\end{pmatrix}
\]

The $\vec{\beta}$ that minimizes $||X \vec{\beta} -
\vec{\gamma}||_2^2$ results in a set of image locations on the plane
that best honors all the SIFT-based distance measurements between
images. In practice there are often cases where there is a break in
the chain of images, meaning that no SIFT matches were found between
one segment of the plane and another. In this case we add rows to the
$A$ matrix and observations to the $\vec{\gamma}$ vector that contain
the original noisy $x$ and $y$ distance estimates generated by the
localization algorithm \cite{chen2010indoor, liu2010indoor}. Another
way to do this is to add rows for all neighboring pairs of images and
solve a weighted least squares problem where the SIFT distances are
given a higher weight i.e. 1, and the noisy distances generated by the
localization algorithm \cite{chen2010indoor, liu2010indoor} are given
a smaller weight i.e. 0.01.

After completing this same process for the $y$ dimension as well, and
making the resultant shifts, our images overlap and match each other
with far greater accuracy. Applying the tile caching method from
Section \ref{sec:mappingWithCaching} on these re-localized images
results in the significant improvements shown in Figure
\ref{fig:compareAll}(c), as compared to Figure \ref{fig:compareAll}(b).

\subsection{Seam Minimization}
\label{sec:seamMinimization}

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{projectionWall.jpg}}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{projectionCeiling.jpg}}
  \caption{(a): Undistorted fisheye images for vertical planes such as
    walls are tilted, but their effective camera axis is more or less
    normal to the plane. (b): The effective camera axis for ceilings
    is at an angle with respect to the plane normal.}
  \label{fig:projectionAngles}
\end{figure}

As mentioned earlier, the mobile backpack system used to capture data
in this paper contains 2 cameras with $180^\circ$ fisheye lenses
facing to the right and left. Since most human operators do not carry
the backpack in a perfectly upright position and are bent forwards at
15 to 20 degrees with respect to the vertical direction, the
undistorted fisheye images are head on with respect to vertical walls,
but at an angle with respect to horizontal floors and ceilings. This
is depicted in Figure \ref{fig:projectionAngles}.

These oblique camera angles translate into textures that span
extremely large areas once projected. Using the tile-based texture
mapping criteria from Figure \ref{fig:scoringFunction}, such
projections have good scores for certain areas on the plane, but worse
scores for others. The tiling approach in Section
\ref{sec:simpleTextureMapping} is thus a good choice for texturing
floors and ceilings, as it uses the parts of image projections that
are good choices for their respective plane locations, e.g. areas near
point A in Figure \ref{fig:projectionAngles}(b), but not near point B.

For wall planes however, most images are taken from close distances
and more or less head-on angles, resulting in higher resolution
fronto-parallel projections. As a result, for each tile on a wall
plane, the cost function of Figure \ref{fig:scoringFunction} is
relatively flat with respect to a large number of captured images, as
they are all more or less head on. Thus it is conceivable to use a
different texturing strategy for walls so as to minimize the visible
seams for texture mapped planes. One way to do so is to choose the
smallest possible set of images that (a) covers the entire plane and
(b) minimizes the amount of visible seams. A straigntforward cost
function that accomplishes the latter is the sum of squared pixel
differences in overlapping regions between all pairs of images, after
they have been aligned as described in Section
\ref{sec:projectionAndRotation}. Minimizing this cost function, which
we refer to as SSD, encourages image boundaries to occur either in
featureless areas, such as bare walls, or in areas where images match
extremely well.

To cover the entirety of a plane, our problem can be defined as
minimally covering a polygon i.e. the plane, using other polygons of
arbitrary geometry i.e. image projections, with the added constraint
of minimizing the cost function between chosen images.  This is a
complex problem, though we can take a number of steps to simplify
it. Given that wall-texture candidate images are taken from more or
less head-on angles, and assuming only minor rotations are made during
localization refinement, we can reason that their projections onto the
plane are approximately rectangular. By cropping them all to be
rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
problem becomes the conceptually simpler one of filling a polygon with
rectangles, such that the sum of all costs between each pair of
rectangles is minimal. We thus also retain the advantages of working
with rectangular units, as explained in Section
\ref{sec:simpleTextureMapping}.

The location and orientation of the cameras on the acquisition
backpack is such that images nearly always contain the entirety of the
floor to ceiling range of wall planes. Images are therefore rarely
projected with one above another when texturing wall planes. In
essence, we need only to ensure horizontal coverage of wall planes, as
our images provide full vertical coverage themselves. We can thus
construct a Directed Acyclic Graph (DAG) from the images, with edge
costs defined by the SSD cost function, and solve a simple shortest
path problem to find an optimal subset of images with regard to the
cost function \cite{dijkstra}.

@@

Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
from overlapping images of a long hallway. Images are sorted by
horizontal location left to right, and become nodes in a
graph. Directed edges are placed in the graph from left to right
between images that overlap. The weights of these edges are determined
by the SSD cost function. Next, we add two
artificial nodes, one start node representing the left border of the
plane, and one end node representing the right border of the
plane. The left(right) artificial node has directed edges with equal
cost $C_0$ to(from) all images that meet the left(right) border of the
plane.

@@

In rare cases where the vertical dimension of the plane is not
entirely covered by one or more chosen images, we are left with holes
where no images are selected to texture. To address this, we solve for a new shortest path after modifying the edges chosen by the original shortest path solution such that they
have higher cost than all other edges in our DAG, and solve for a new
shortest path. This ensures that these edges are not chosen again
unless they are the only available option. Our second shortest path
solution results in a new set of chosen images, of which we only
retain those that cover areas not covered by the first set. This
process can be repeated as many times as needed, until holes are no
longer present. This method is not as optimal as a 2D-coverage
solution would be, but it is a fast approximation, and adequately
handles the few holes we encounter.

With this completed, we have now mapped every location on the plane to
at least one image, and have minimized the number of images, as well
as the discontinuities between their borders. Figures \ref{fig:compareAll}(c) and
\ref{fig:compareAll}(d) compare the tile caching method against this
seam minimization method. For the latter, we arbitrarily choose one image for texturing where images overlap. Though both methods provide aligned texturing, the seam minimization approach results in fewer
visible discontinuities, since it directly reduces the cost of each
image boundary, while the tile caching method uses a scoring function
that only approximates this effect. Furthermore, seam minimization
guarantees the best selection of images, while the sequential tile
caching method may select images early on that turn out to be poor
choices once subsequent tiles have been processed. The seam
minimization approach is also less intensive in terms of memory usage
and runtime, as it does not require discretizing planes or images.

In the context of texturing an entire 3D planar model, we apply the seam
minimization approach on walls, due to its superior output when
provided with head-on images. Floors and ceilings however, given their
many images taken at oblique angles, are textured using the tile caching method.

\subsection{Blending}
\label{sec:blending}
We now apply the same blending process to the two texturing methods:
localization refinement followed by either tile caching or seam
minimization.

Although the preprocessing steps and image selection in both methods
attempt to minimize all mismatches between images, there are occasional
unavoidable discontinuities in the final texture due to different
lighting conditions or inaccuracies in planar geometry or
projection. These can however be treated and smoothed over by applying
alpha blending over image seams.  Whether the units we are blending
are rectangularly-cropped images or rectangular tiles, we can apply
the same blending procedure, as long as we have a guaranteed overlap
between units to blend over.

For the tile caching method, we can ensure overlap by texturing a
larger tile than needed for display. For example, for a rendered tile
$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
\times (l_1 + l_2)$ in size. For the seam minimization method, we have
already ensured overlap between images. To enforce consistent blending
however, we add a minimuum required overlap distance while solving the
shortest path problem in Section
\ref{sec:seamMinimization}. Additionally, if images overlap in a region
greater than the overlap distance, we only apply blending over an area
equal to the overlap distance.

After blending pixels linearly across overlapping regions using alpha
blending, texture mapping is complete. Figure
\ref{fig:pipelineimages} shows each incremental step of our texture
mapping approach for a different wall, as well as the final blended output resulting from
both of our methods.

@@

\section{Results and Conclusions}
\label{sec:resultsAndConclusions}
In this paper, we have developed an approach to texture map models
with noisy camera localization data. We are able to refine image
locations based on feature matching, and robustly handle outliers. The tile-based mapping approach can be used to texture both simple rectangular walls as
well as complex floor and ceiling geometry. We also presented a seam minimization texturing method that produces seamless textures on planes where
multiple head-on images are available. Each of these approaches is
highly modular, and easily tunable for different environments and
acquisition hardware.

Examples of ceilings and floors textured with the tile caching approach, and walls
textured with the seam minimization approach, are displayed in Figure
\ref{fig:results}. High resolution texture comparisons, as well as a
walkthrough of a fully textured 3D model are available in the
accompanying video to this paper.
